### 2020-04-20 papers-vol-1.tex
Fix names and some weird word/entry splitting issues

\insertmydocument{chapter}{Strength of Reasons for Moral Dissent}{James Freeman}{pdfs/long/9longFreeman.doc.pdf}
\insertmydocument{chapter}{What is Peculiar about Moral Dissent? Commentary on Freeman’s ``Strength of Reasons for Moral Dissent''}{John Patrick Casey}{pdfs/commentary/9longFreeman-C.docx.pdf}

@@

\insertmydocument{chapter}{“’I said what I said’ - Black Women and Argumentative Politeness Norms”}{Tempest M Henning}{pdfs/long/13longHenning.docx.pdf}
\insertmydocument{chapter}{Commentary on Tempest Henning’s “’I Said What I Said’ - Black Women and Argumentative Politeness Norms”}{Catherine Hundleby}{pdfs/commentary/13longHenning-C.doc.pdf}

@@

\insertmydocument{chapter}{Disagreement, Public Reasoning, and (Non-)Authoritarian Argumentation}{Karim Sadek}{pdfs/long/23longSadek.doc.pdf}
\insertmydocument{chapter}{Commentary on Sadek’s Disagreement, Public Reasoning, and (Non-)Authoritarian Argumentation}{Cristina Corredor}{pdfs/commentary/23longSadek-C.doc.pdf}

@@

\insertmydocument{chapter}{Profiling Dialogues: Multi-trait Mapping of Televised Argumentative Exchanges}{G\'{a}bor \'{A} Zempl\'{e}n}{pdfs/long/27longZemplen.doc.pdf}
\insertmydocument{chapter}{Commentary on Zempl\'{e}n’s Profiling Dialogues: Multi-trait Mapping of Televised Argumentative Exchanges}{Mehmet Ali \"{U}zelg\"{u}n}{pdfs/commentary/27longZemplen-C.doc.pdf}

@@

\insertmydocument{chapter}{Visual Argument Schemes in the PTA}{Leo Groarke}{pdfs/thematic/1regularthematicGroarke.docx.pdf}
\insertmydocument{chapter}{The Prospects for Multimodal Schemes of Argument: Assessing the Spoofing Strategies in Subvertisements of the Tobacco Industry
}{Assimakis Tseronis}{pdfs/thematic/3regularThematicTseronis.docx.pdf}
\insertmydocument{chapter}{(Mis)Framing Photographs as an Obstacle to Fair Dissent}{Marta Zampa, Chiara Pollaroli}{pdfs/thematic/4regularThematicZampa.docx.pdf}
\insertmydocument{chapter}{Dissent, Disadvantage, Testimony and the Ideological ‘Truth’ of Presumptions}{Harmony Peach}{pdfs/thematic/5regularThematicPeach.doc.pdf}
\insertmydocument{chapter}{With All Due Respect: Controversial Beliefs and the Limits of Responsible Argumentation}{Tracy Bowell}{pdfs/thematic/7regularThematicBowell.doc.pdf}
\insertmydocument{chapter}{A Quantitative Corpus-Based Study of Evidentiality and Disagreement in Earnings Conference Calls}{Andrea Rocci, Carlo Raimondo, Daniele Puccinelli}{pdfs/thematic/9regularThematicRocci.docx.pdf}
\insertmydocument{chapter}{Five Approaches to Argument Strength: Probabilistic, Dialectical, Structural, Empirical, and Computational}{Frank Zenker, David Godden, Marcin Selinger, Simon Wells, Kamila Debowska-Kozlowska}{pdfs/thematic/13regularThematicZenkeretal.docx.pdf}
\insertmydocument{chapter}{Responsible Agent Deliberation}{Douglas Walton, Alice Toniolo}{pdfs/thematic/18regularThematicWalton.doc.pdf}
\insertmydocument{chapter}{From Dialogic to Argument-Based Teaching: Introducing Pragmatic Criteria to Analyse Whole-Class Interactions}{Chrysi Rapanta, Dilar Cascalheira}{pdfs/thematic/20regularThematicRapanta.doc.pdf}

>>>>

\insertmydocument{chapter}{Strength of Reasons for Moral Dissent}{James B. Freeman}{pdfs/long/9longFreeman.doc.pdf}
\insertmydocument{chapter}{What is Peculiar about Moral Dissent? Commentary on Freeman’s ``Strength of Reasons for Moral Dissent''}{John Patrick Casey}{pdfs/commentary/9longFreeman-C.docx.pdf}

@@

\insertmydocument{chapter}{“’I said what I said’ - Black Women and Argumentative Politeness Norms”}{Tempest M. Henning}{pdfs/long/13longHenning.docx.pdf}
\insertmydocument{chapter}{Commentary on Tempest Henning’s “’I Said What I Said’ - Black Women and Argumentative Politeness Norms”}{Catherine Hundleby}{pdfs/commentary/13longHenning-C.doc.pdf}

@@

\insertmydocument{chapter}{Disagreement, Public Reasoning, and (Non-)Authoritarian Argumentation}{Karim Sadek}{pdfs/long/23longSadek.doc.pdf}
\insertmydocument{chapter}{Commentary on Sadek’s Disagreement, Public Reasoning, and\\(Non-)Authoritarian Argumentation}{Cristina Corredor}{pdfs/commentary/23longSadek-C.doc.pdf}

@@

\insertmydocument{chapter}{Profiling Dialogues: Multi-trait Mapping of Televised Argumentative Exchanges}{G\'{a}bor \'{A}. Zempl\'{e}n}{pdfs/long/27longZemplen.doc.pdf}
\insertmydocument{chapter}{Commentary on Zempl\'{e}n’s Profiling Dialogues: Multi-trait Mapping of Televised Argumentative Exchanges}{Mehmet Ali \"{U}zelg\"{u}n}{pdfs/commentary/27longZemplen-C.doc.pdf}

@@

\insertmydocument{chapter}{Visual Argument Schemes in the PTA}{Leo Groarke}{pdfs/thematic/1regularthematicGroarke.docx.pdf}
\insertmydocument{chapter}{The Prospects for Multimodal Schemes of Argument: Assessing the Spoofing Strategies in Subvertisements of the Tobacco Industry
}{Assimakis Tseronis}{pdfs/thematic/3regularThematicTseronis.docx.pdf}
\insertmydocument{chapter}{(Mis)Framing Photographs as an Obstacle to Fair Dissent}{Marta Zampa, Chiara Pollaroli}{pdfs/thematic/4regularThematicZampa.docx.pdf}
\insertmydocument{chapter}{Dissent, Disadvantage, Testimony and the Ideological ‘Truth’ of Presumptions}{Harmony Peach}{pdfs/thematic/5regularThematicPeach.doc.pdf}
\insertmydocument{chapter}{With All Due Respect: Controversial Beliefs and the Limits of Responsible Argumentation}{Tracy Bowell}{pdfs/thematic/7regularThematicBowell.doc.pdf}
\insertmydocument{chapter}{A Quantitative Corpus-Based Study of Evidentiality and Disagreement in Earnings Conference Calls}{Andrea Rocci, Carlo Raimondo, Daniele Puccinelli}{pdfs/thematic/9regularThematicRocci.docx.pdf}
\insertmydocument{chapter}{Five Approaches to Argument Strength: Probabilistic, Dialectical, Structural, Empirical, and Computational}{Frank Zenker, Kamila Debowska-Kozlowska, David Godden, Marcin Selinger, Simon Wells}{pdfs/thematic/13regularThematicZenkeretal.docx.pdf}
\insertmydocument{chapter}{Responsible Agent Deliberation}{Douglas Walton, Alice Toniolo}{pdfs/thematic/18regularThematicWalton.doc.pdf}
\insertmydocument{chapter}{From Dialogic to Argument-Based Teaching: Introducing Pragmatic Criteria to Analyse Whole-Class Interactions}{Chrysi Rapanta, Dilar Cascalheira}{pdfs/thematic/20regularThematicRapanta.doc.pdf}

### 2020-04-20 papers-vol-2.tex
Fix names and some weird word/entry splitting issues

\insertmydocument{chapter}{Heroic Argumentation: On Heroes, Heroism, and Glory in Arguments}{John Casey, Daniel Cohen}{pdfs/regular/18regularCasey.doc.pdf} % 18

@@

\insertmydocument{chapter}{Devil’s Advocates are the Angels of Argumentation}{Katharina Stevens, Daniel Cohen}{pdfs/regular/21regularCohen.docx.pdf} % 21

@@

\insertmydocument{chapter}{The Pragma-dialectical View of Comparison Argumentation}{Frans van Eemeren, Bart Garssen}{pdfs/regular/31regularEemeren.doc.pdf} % 31

@@

@@

\insertmydocument{chapter}{Argument Scheme Theory}{Hans V Hansen}{pdfs/regular/45regularHansen.docx.pdf} % 45

@@

\insertmydocument{chapter}{Argument, Justification and Inquiry: a Pragmatist Approach}{Federico Ezequiel L\'{o}pez}{pdfs/regular/75regularLopez.doc.pdf} % 75

>>>>

\insertmydocument{chapter}{Heroic Argumentation: On Heroes, Heroism, and Glory in Arguments}{John Casey, Daniel H. Cohen}{pdfs/regular/18regularCasey.doc.pdf} % 18

@@

\insertmydocument{chapter}{Devil’s Advocates are the Angels of Argumentation}{Katharina Stevens, Daniel H. Cohen}{pdfs/regular/21regularCohen.docx.pdf} % 21

@@

\insertmydocument{chapter}{The Pragma-dialectical View of Comparison Argumentation}{Frans H. van Eemeren, Bart Garssen}{pdfs/regular/31regularEemeren.doc.pdf} % 31

@@

\addtocontents{toc}{\protect\newpage}

@@

\insertmydocument{chapter}{Argument Scheme Theory}{Hans V. Hansen}{pdfs/regular/45regularHansen.docx.pdf} % 45

@@

\insertmydocument{chapter}{Argument, Justification and Inquiry: a Pragmatist Approach}{Federico E. L\'{o}pez}{pdfs/regular/75regularLopez.doc.pdf} % 75
